Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
math mode table 2
caption table 2
edit appendix

We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (i.e, the quantizer includes any digital gain added in the code).
The process of quantization in the DAC is similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac} \rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $. If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
From the above equations we can now define the ADC and DAC quantization noises, ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], {\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$ where $q_1=q_{c} \wedge q_2=q_{dac}$. Note that this is shown in fig. \ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC and $Q_2$ the quantizer for the DAC.
These bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
The resulting dynamics are:
\begin{align}
\label{eq:pre_quantization}
{x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k),\\
u_k&=-K{x}_{k}+{{\nu}_1}_k. 
\end{align}

@@

\caption{Benchmarks for State-Space Physical Plants.}

@@

\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & -0.05 & 0.03125 & 0.032 & 0 \\ \hline

@@

>>>>

We will assume, for the purposes of this analysis, that the domain of the
ADC is that of the digital controller (i.e, the quantizer includes any
digital gain added in the code).  The process of quantization in the DAC is
similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
resolution in higher than the ADCs, then the DAC quantization error is equal
to zero.  From the above equations we can now define the ADC and DAC
quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$ where $q_1=q_{c} \wedge
q_2=q_\mathit{dac}$.  This is illustrated in
Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
whether the noise is correlated, hence we may use them to over-approximate
the effect of the noise on the state space progression over time.  The
resulting dynamics are:
%
\begin{align}
\label{eq:pre_quantization}
{x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k),\\
u_k&=-K{x}_{k}+{{\nu}_1}_k. 
\end{align}

@@

@@

\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & $-0.05$ & $0.03125$ & $0.032$ & $0$ \\ \hline

@@

\caption{Benchmarks for State-Space Physical Plants}
